---
title: "Comparison of Foraging Activity for Rockfish Complexes"
author: "Sara Michele Schaal"
date: "1/24/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r include = FALSE}
## Load Relevant Packages
    # if(!("plyr" %in% installed.packages())){
    #   install.packages("plyr")
    # }
    # if(!("dplyr" %in% installed.packages())){
    #   install.packages("dplyr")
    # }
    # if(!("ggplot2" %in% installed.packages())){
    #   install.packages("ggplot2")
    # }
    # if(!("scales" %in% installed.packages())){
    #   install.packages("scales")
    # }
    # if(!("sm" %in% installed.packages())){
    #   install.packages("sm")
    # }
    # if(!("ggpubr" %in% installed.packages())){
    #   install.packages("ggpubr")
    # }

    library(plyr)
    library(dplyr)
    library(ggplot2)
    library(scales)
    library(ggpubr)
 #   library(sm)
    
```

## Read in data and manipulate
```{r}

  full.act <- read.csv("data/Activity/20171129_ActivityData.csv")
  black.temps <- read.csv("data/black_exp_temps.csv")
  copper.temps <- read.csv("data/copper_exp_temps.csv")

  # Subset data into two experiments  
  black.act <- full.act[full.act$Species == "Black", ]
  copper.act <- full.act[full.act$Species == "Copper", ]
  
  # Reorder data to be in numerical ascending order 
  # **(only way for loop to work properly)
  black.temps.asc <- black.temps[order(black.temps$Bucket), ]
  copper.temps.asc <- copper.temps[order(copper.temps$Bucket_ID), ]
  
  # Fill in actual mean temperature data from experiment
  # BY complex
  for(i in 1:16){
    for(j in 1:nrow(black.act)){
      if(black.act$Bucket[j] == i){
        black.act$Temperature[j] <- black.temps.asc$mean[i]
      }
    }
  }
  
  # CQ complex
  for(i in 1:16){
    for(j in 1:nrow(copper.act)){
      if(copper.act$Bucket[j] == i){
        copper.act$Temperature[j] <- copper.temps.asc$mean[i]
      }
    }
  }

  
  # take the mean of the two watches of the same fish per viewer
  black.act$Act_Mean_Julia <- rowMeans(black.act[, 8:9])
  black.act$Act_Mean_Sandi <- rowMeans(black.act[, 10:11])
  copper.act$Act_Mean_Julia <- rowMeans(copper.act[,8:9])
  copper.act$Act_Mean_Sandi <- rowMeans(copper.act[,10:11])
  

```



## Calculate averages per bucket per timepoint
```{r}

### Black Rockfish ###

    # create empty data frames for mean bucket activity values
    Mean.Activity <- matrix(NA, nrow(unique(black.act[c("Date", "AM_PM", "Bucket")])),4)
    bucket.act.average <- unique(black.act[c("Date", "AM_PM", "Bucket", "Temperature")])
    complete.act.data <- cbind(bucket.act.average, Mean.Activity)
    colnames(complete.act.data) <- c("Date", "AM_PM", "Bucket", "Temperature", 
                                     "mean.julia", "mean.sandi", "mean.both", "FishAlive")
    
    # initialize the vectors that will be used in the forloop ** NOTE data in these 
    # vectors is written over in each loop.. they are TEMPORARY vectors **
    bucket.act.julia <- NULL
    bucket.act.sandi <- NULL
    bucket.act.both <- NULL
    
    # initialize the counter for stepping through the output matrix
    j <- 1
    # For loop to step through data frame to get activity averages
    for(i in 1:nrow(black.act)){
      
      # looping through majority of data to grab all those rows that are not the last row
      # but are all those that equal the same bucket from the same day and getting 
      # activity averages
      if(i != nrow(black.act) && i == 1 || 
         black.act$Bucket[i] == black.act$Bucket[i-1] && i != nrow(black.act)){
        
        bucket.act.julia <- c(bucket.act.julia, black.act$Act_Mean_Julia[i])
        bucket.act.sandi <- c(bucket.act.sandi, black.act$Act_Mean_Sandi[i])
        bucket.act.both <- c(bucket.act.both, black.act$Act_Mean_Julia[i], black.act$Act_Mean_Sandi[i])
     
        # special case for last row 
       } else {
         if(i == nrow(black.act)){

          # Remove any NAs before taking mean for a bucket at a timepoint
          bucket.act.both.noNA <- bucket.act.both[!is.na(bucket.act.both)]
          bucket.act.julia.noNA <- bucket.act.julia[!is.na(bucket.act.julia)]
          bucket.act.sandi.noNA <- bucket.act.sandi[!is.na(bucket.act.sandi)]
          complete.act.data$mean.julia[j] <- sum(bucket.act.julia.noNA)/length(bucket.act.julia.noNA)
          complete.act.data$mean.sandi[j] <- sum(bucket.act.sandi.noNA)/length(bucket.act.sandi.noNA)
          complete.act.data$mean.both[j] <- sum(bucket.act.both.noNA)/length(bucket.act.both.noNA)
          complete.act.data$FishAlive[j] <- length(bucket.act.sandi.noNA)
          j <- j + 1
          
        } else {
          
          # Remove any NAs before taking mean for a bucket at a timepoint
          bucket.act.both.noNA <- bucket.act.both[!is.na(bucket.act.both)]
          bucket.act.julia.noNA <- bucket.act.julia[!is.na(bucket.act.julia)]
          bucket.act.sandi.noNA <- bucket.act.sandi[!is.na(bucket.act.sandi)]
          
          # Take mean of that bucket for that day and insert into complete.data dataframe
          complete.act.data$mean.julia[j] <- sum(bucket.act.julia.noNA)/length(bucket.act.julia.noNA)
          complete.act.data$mean.sandi[j] <- sum(bucket.act.sandi.noNA)/length(bucket.act.sandi.noNA)
          complete.act.data$mean.both[j] <- sum(bucket.act.both.noNA)/length(bucket.act.both.noNA)
          complete.act.data$FishAlive[j] <- length(bucket.act.sandi.noNA)
          bucket.act.julia <- black.act$Act_Mean_Julia[i]
          bucket.act.sandi <- black.act$Act_Mean_Sandi[i]
          bucket.act.both <- c(black.act$Act_Mean_Julia[i], black.act$Act_Mean_Sandi[i])
          # counter to step through inputting data into the complete.data dataframe
          j <- j + 1
          
        } # close else
       } # close if else
      } # close for loop
    
### Copper Rockfish ###
    
    # create empty data frames for mean bucket activity values
    Mean.Activity.cp <- matrix(NA, nrow(unique(copper.act[c("Date", "AM_PM", "Bucket")])),4)
    bucket.act.average.cp <- unique(copper.act[c("Date", "AM_PM", "Bucket", "Temperature")])
    complete.act.data.cp <- cbind(bucket.act.average.cp, Mean.Activity.cp)
    colnames(complete.act.data.cp) <- c("Date", "AM_PM", "Bucket", "Temperature", 
                                     "mean.julia", "mean.sandi", "mean.both", "FishAlive")
    
    # initialize the vectors that will be used in the for loop ** NOTE data in these vectors is written
    # over in each loop.. they are TEMPORARY vectors **
    bucket.act.julia.cp <- NULL
    bucket.act.sandi.cp <- NULL
    bucket.act.both.cp <- NULL
    
    bucket.act.both.noNA.cp <- NULL
    bucket.act.julia.noNA.cp <- NULL
    bucket.act.sandi.noNA.cp <- NULL
    
    # initialize the counter for stepping through the output matrix
    j <- 1
    i <- 1
    # For loop to step through data frame to get activity averages
    for(i in 1:nrow(copper.act)){
      
      # looping through majority of data to grab all those rows that are not the last row
      # but are all those that equal the same bucket from the same day and getting activity averages
      if(i != nrow(copper.act) && i == 1 || 
         copper.act$Bucket[i] == copper.act$Bucket[i-1] && i != nrow(copper.act)){
        
        bucket.act.julia.cp <- c(bucket.act.julia.cp, copper.act$Act_Mean_Julia[i])
        bucket.act.sandi.cp <- c(bucket.act.sandi.cp, copper.act$Act_Mean_Sandi[i])
        bucket.act.both.cp <- c(bucket.act.both.cp, copper.act$Act_Mean_Julia[i], copper.act$Act_Mean_Sandi[i])
     
        # special case for last row 
       } else {
         if(i == nrow(copper.act)){

          # Remove any NAs before taking mean for a bucket at a timepoint
          bucket.act.both.noNA.cp <- bucket.act.both.cp[!is.na(bucket.act.both.cp)]
          bucket.act.julia.noNA.cp <- bucket.act.julia.cp[!is.na(bucket.act.julia.cp)]
          bucket.act.sandi.noNA.cp <- bucket.act.sandi.cp[!is.na(bucket.act.sandi.cp)]
          complete.act.data.cp$mean.julia[j] <- sum(bucket.act.julia.noNA.cp)/length(bucket.act.julia.noNA.cp)
          complete.act.data.cp$mean.sandi[j] <- sum(bucket.act.sandi.noNA.cp)/length(bucket.act.sandi.noNA.cp)
          complete.act.data.cp$mean.both[j] <- sum(bucket.act.both.noNA.cp)/length(bucket.act.both.noNA.cp)
          complete.act.data.cp$FishAlive[j] <- length(bucket.act.sandi.noNA.cp)
          j <- j + 1
          
        } else {
          
          # Remove any NAs before taking mean for a bucket at a timepoint
          bucket.act.both.noNA.cp <- bucket.act.both.cp[!is.na(bucket.act.both.cp)]
          bucket.act.julia.noNA.cp <- bucket.act.julia.cp[!is.na(bucket.act.julia.cp)]
          bucket.act.sandi.noNA.cp <- bucket.act.sandi.cp[!is.na(bucket.act.sandi.cp)]
          
          # Take mean of that bucket for that day and insert into complete.data dataframe
          complete.act.data.cp$mean.julia[j] <- sum(bucket.act.julia.noNA.cp)/length(bucket.act.julia.noNA.cp)
          complete.act.data.cp$mean.sandi[j] <- sum(bucket.act.sandi.noNA.cp)/length(bucket.act.sandi.noNA.cp)
          complete.act.data.cp$mean.both[j] <- sum(bucket.act.both.noNA.cp)/length(bucket.act.both.noNA.cp)
          complete.act.data.cp$FishAlive[j] <- length(bucket.act.sandi.noNA.cp)
          bucket.act.julia.cp <- copper.act$Act_Mean_Julia[i]
          bucket.act.sandi.cp <- copper.act$Act_Mean_Sandi[i]
          bucket.act.both.cp <- c(copper.act$Act_Mean_Julia[i], copper.act$Act_Mean_Sandi[i])
          # counter to step through inputting data into the complete.data dataframe
          j <- j + 1
          
        } # close else
       } # close if else
      } # close for loop
    
```



## Create a column for Days Since the Start of Experiment
```{r}

### Black Rockfish ###
  # make column for days since start of experiment for panel headers
  complete.act.data$Days_Since_Start <- NA
  
  # add a column that is Date with time of day
  complete.act.data$Date <- as.factor(complete.act.data$Date)
  complete.act.data$Date_Time <- as.factor(paste(complete.act.data$Date, complete.act.data$AM_PM))
   
  # Round temperature data to one significant figure after decimal place
  complete.act.data$RTemperature <- round(complete.act.data$Temperature, 1)
  complete.act.data$DayNum <- NA
  # add in days since start of experiment column
  for(i in 1:length(complete.act.data$Days_Since_Start)){
    if (complete.act.data$Date_Time[i] == "20150623 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 4 AM"
      complete.act.data$DayNum[i] <- 1
    } else if (complete.act.data$Date_Time[i] == "20150624 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 5 PM"
      complete.act.data$DayNum[i] <- 2
    } else if (complete.act.data$Date_Time[i] == "20150625 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 6 AM"
      complete.act.data$DayNum[i] <- 3
    } else if (complete.act.data$Date_Time[i] == "20150625 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 6 PM"
      complete.act.data$DayNum[i] <- 3.5
    } else if (complete.act.data$Date_Time[i] == "20150626 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 7 AM"
      complete.act.data$DayNum[i] <- 4
    } else if (complete.act.data$Date_Time[i] == "20150626 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 7 PM"
      complete.act.data$DayNum[i] <- 4.5
    } else if (complete.act.data$Date_Time[i] == "20150627 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 8 AM"
      complete.act.data$DayNum[i] <- 5
    } else if (complete.act.data$Date_Time[i] == "20150627 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 8 PM"
      complete.act.data$DayNum[i] <- 5.5
    } else if (complete.act.data$Date_Time[i] == "20150628 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 9 AM"
      complete.act.data$DayNum[i] <- 6
    } else if (complete.act.data$Date_Time[i] == "20150628 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 9 PM"
      complete.act.data$DayNum[i] <- 6.5
    } else if (complete.act.data$Date_Time[i] == "20150629 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 10 AM"
      complete.act.data$DayNum[i] <- 7
    } else if (complete.act.data$Date_Time[i] == "20150629 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 10 PM"
      complete.act.data$DayNum[i] <- 7.5
    } else if (complete.act.data$Date_Time[i] == "20150630 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 11 AM"
      complete.act.data$DayNum[i] <- 8
    } else if (complete.act.data$Date_Time[i] == "20150630 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 11 PM"
      complete.act.data$DayNum[i] <- 8.5
    } else if (complete.act.data$Date_Time[i] == "20150702 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 13 AM"
      complete.act.data$DayNum[i] <- 10
    } else if (complete.act.data$Date_Time[i] == "20150702 PM"){
      complete.act.data$Days_Since_Start[i] <- "Day 13 PM"
      complete.act.data$DayNum[i] <- 10.5
    } else if(complete.act.data$Date_Time[i] == "20150703 AM"){
      complete.act.data$Days_Since_Start[i] <- "Day 14 AM"
      complete.act.data$DayNum[i] <- 11
  }
}
### Copper Rockfish ###
  # Make column for Day Since Start of Experiment
  complete.act.data.cp$Days_Since_Start <- NA
  
  # add a column for date time unique combinations
  complete.act.data.cp$Date <- as.factor(complete.act.data.cp$Date)
  complete.act.data.cp$Date_Time <- as.factor(paste(complete.act.data.cp$Date, complete.act.data.cp$AM_PM))
  #complete.act.data.cp[157,9] <- "Day 10 AM" #I am not sure why this single value is going in wrong
  #complete.act.data.cp[157,10] <- "20150714 AM"
   
  # Round temperature data to one significant figure after decimal place
   complete.act.data.cp$RTemperature <- round(complete.act.data.cp$Temperature, 1)
   complete.act.data.cp$DayNum <- NA
   
  # add in days since start of experiment column
  for(i in 1:length(complete.act.data.cp$Days_Since_Start)){
    if (complete.act.data.cp$Date_Time[i] == "20150709 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 5 AM"
      complete.act.data.cp$DayNum[i] <- 1
    } else if (complete.act.data.cp$Date_Time[i] == "20150709 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 5 PM"
      complete.act.data.cp$DayNum[i] <- 1.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150710 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 6 AM"
      complete.act.data.cp$DayNum[i] <- 2
    } else if (complete.act.data.cp$Date_Time[i] == "20150710 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 6 PM"
      complete.act.data.cp$DayNum[i] <- 2.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150711 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 7 AM"
      complete.act.data.cp$DayNum[i] <- 3
    } else if (complete.act.data.cp$Date_Time[i] == "20150711 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 7 PM"
      complete.act.data.cp$DayNum[i] <- 3.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150712 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 8 AM"
      complete.act.data.cp$DayNum[i] <- 4
    } else if (complete.act.data.cp$Date_Time[i] == "20150712 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 8 PM"
      complete.act.data.cp$DayNum[i] <- 4.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150713 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 9 AM"
      complete.act.data.cp$DayNum[i] <- 5
    } else if (complete.act.data.cp$Date_Time[i] == "20150713 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 9 PM"
      complete.act.data.cp$DayNum[i] <- 5.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150714 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 10 AM"
      complete.act.data.cp$DayNum[i] <- 6
    } else if (complete.act.data.cp$Date_Time[i] == "20150715 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 11 AM"
      complete.act.data.cp$DayNum[i] <- 7
    } else if (complete.act.data.cp$Date_Time[i] == "20150715 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 11 PM"
      complete.act.data.cp$DayNum[i] <- 7.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150716 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 12 AM"
      complete.act.data.cp$DayNum[i] <- 8
    } else if (complete.act.data.cp$Date_Time[i] == "20150716 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 12 PM"
      complete.act.data.cp$DayNum[i] <- 8.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150717 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 13 AM"
      complete.act.data.cp$DayNum[i] <- 9
    } else if (complete.act.data.cp$Date_Time[i] == "20150717 PM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 13 PM"
      complete.act.data.cp$DayNum[i] <- 9.5
    } else if (complete.act.data.cp$Date_Time[i] == "20150718 AM"){
      complete.act.data.cp$Days_Since_Start[i] <- "Day 14 AM"
      complete.act.data.cp$DayNum[i] <- 10
    }
  }

```



## Panel Plot Activity Across Temperatures for Every Date
```{r}
################################################################
#### Factor Days ###############################################
#### to change to correct order for plotting the panel plot ####
################################################################
### black
  b.unique_Days <- c("Day 4 AM", "Day 5 PM", "Day 6 AM", "Day 6 PM", "Day 7 AM", "Day 7 PM", 
                      "Day 8 AM", "Day 8 PM", "Day 9 AM", "Day 9 PM", "Day 10 AM", "Day 10 PM", 
                      "Day 11 AM", "Day 11 PM", "Day 13 AM", "Day 13 PM", "Day 14 AM")
  complete.act.data$Days_Since_Start <- as.factor(complete.act.data$Days_Since_Start)
  complete.act.data$Days_Since_Start <- factor(complete.act.data$Days_Since_Start, 
                                               levels = b.unique_Days)
### copper
   c.unique_Days <- c("Day 5 AM", "Day 5 PM", "Day 6 AM", "Day 6 PM", "Day 7 AM", "Day 7 PM",  
                       "Day 8 AM", "Day 8 PM", "Day 9 AM", "Day 9 PM", "Day 10 AM", "Day 11 AM", 
                       "Day 11 PM", "Day 12 AM", "Day 12 PM", "Day 13 AM", "Day 13 PM", "Day 14 AM")
   complete.act.data.cp$Days_Since_Start <- as.factor(complete.act.data.cp$Days_Since_Start)
   complete.act.data.cp$Days_Since_Start <- factor(complete.act.data.cp$Days_Since_Start, 
                                                   levels = c.unique_Days)


#############################
#### Black Rockfish Plot ####
############################# 
  # Save plot
    day.plot <- ggplot(data=complete.act.data, 
                         aes(x=RTemperature, y=mean.both, 
                            group=as.factor(Days_Since_Start), 
                            color = as.integer(Date_Time))) + 
                       geom_point(aes(size = complete.act.data$FishAlive), alpha = 0.8) + 
                       geom_smooth(method = "lm", se = FALSE) 
    
  # Create plot 
   bAll.panel <- day.plot + facet_wrap(~Days_Since_Start) +
     labs(y = "Mean Activity", x = "Temperature") +
     scale_color_gradient(low = "gainsboro", high = "black", name = "Time") + 
     theme_bw() + 
     theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(),
           axis.line = element_line(colour = "black"),
           legend.position = "none") + 
     scale_x_continuous(breaks = pretty_breaks()) + 
     #scale_size(range = c(1,3))
     scale_radius(NULL, NULL)
   
##############################
#### Copper Rockfish Plot ####
############################## 
  # Save plot
   day.plot.cp <- ggplot(data=complete.act.data.cp, 
                         aes(x=RTemperature, y=mean.both, 
                            group=as.factor(Days_Since_Start), 
                            color = as.integer(Date_Time))) + 
                  geom_point(aes(size = complete.act.data.cp$FishAlive), alpha = 0.8) + 
                  geom_smooth(method = "lm", se = FALSE) 
  # Create plot
   cpAll.panel <- day.plot.cp + facet_wrap(~Days_Since_Start) + 
     labs(y = "Mean Activity", x = "Temperature") + 
     scale_color_gradient(low = "gainsboro", high = "darkorange", name = "Time") + 
     scale_x_continuous(NULL) +
     theme_bw() + 
     theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(),
           axis.line = element_line(colour = "black"), 
           legend.position = "none")  +
     scale_radius(NULL, NULL)

####################################
#### Black Rockfish Single Plot ####
####################################
  # Create plot
   bAll.single <- day.plot + labs(y = "Mean Activity", x = "Temperature") + 
   scale_color_gradient(low = "gainsboro", high = "black", 
                        name = "Days Since \nStart of \nExperiment", 
                        breaks = c(4, 8, 12, 16), 
                        labels = c("Day 6 PM", "Day 8 AM", "Day 10 PM", "Day 13 PM")) + 
   scale_x_continuous(breaks = pretty_breaks()) +
   theme_bw() + 
   theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         axis.line = element_line(colour = "black")) +
   scale_radius(breaks = c(1,2,3,4), name = "# Fish Alive", limits = c(1,4))  +
   guides(color = guide_colourbar(order = 1),
          size = guide_legend(order = 2))
   
#####################################
#### Copper Rockfish Single Plot ####
#####################################
  # Create plot
   cpAll.single <- day.plot.cp + labs(y = "Mean Activity", x = "Temperature") + 
   scale_color_gradient(low = "gainsboro", high = "darkorange", 
                        name = "Days Since \nStart of \nExperiment", 
                        breaks = c(4, 8, 12, 16), 
                        labels = c("Day 6 PM", "Day 8 AM", "Day 10 AM", "Day 13 PM")) + 
   scale_x_continuous(breaks = pretty_breaks()) +
   theme_bw() + 
   theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         axis.line = element_line(colour = "black")) +
   scale_radius(NULL, NULL) 
   
   ggarrange(bAll.panel, bAll.single, cpAll.panel, cpAll.single, labels = (c("A", "B", "C", "D")))
   
```


## Generalized Linear Model
Testing the three way interaction of Time by Species by Temperature

### First edit date/time to be in POSIX form
```{r}
library(plyr)
#Inspect data elements
str(complete.act.data)

# Construct AM/PM to be times
  complete.act.data$AM_PMTime <- complete.act.data$AM_PM
  complete.act.data$AM_PMTime <- revalue(complete.act.data$AM_PMTime, 
                                         c("AM" = "09:00:00", "PM" = "18:00:00"))
  
  complete.act.data.cp$AM_PMTime <- complete.act.data.cp$AM_PM
  complete.act.data.cp$AM_PMTime <- revalue(complete.act.data.cp$AM_PMTime, 
                                            c("AM" = "09:00:00", "PM" = "18:00:00"))
# Create POSIX
  # black
  complete.act.data$DateTimePOS <- as.POSIXlt(paste(as.Date(as.character(complete.act.data$Date),
                                                            format = ("%Y%m%d")),
                                                    as.character(complete.act.data$AM_PMTime)))
  # copper
  complete.act.data.cp$DateTimePOS <- as.POSIXlt(paste(as.Date(as.character(complete.act.data.cp$Date), 
                                                               format = ("%Y%m%d")),
                                                       as.character(complete.act.data.cp$AM_PMTime)))
```


### Add column to delineate between species complexes and combined two dataframes
```{r}

##################################
#### Data Manipulation ###########
### Combine Species DataFrames ###
  species <- rep("Black", 259)
  species.cp <- rep("Copper", 271)
  complete.act.data.sp <- cbind(complete.act.data, species)
  complete.act.data.cp.sp <- cbind(complete.act.data.cp, species.cp)
  colnames(complete.act.data.cp.sp)[15] <- "species"
  full.act.data <- rbind(complete.act.data.sp,complete.act.data.cp.sp)
  
```

### Run model and check assumptions
```{r}
  
###################################################
### Full Model: species*temp*time 3-way interaction
    species.act.m1 <- lm(full.act.data$mean.both ~
                         full.act.data$Temperature*as.numeric(full.act.data$DateTimePOS)*full.act.data$species)
    summary(species.act.m1)
  
    Anova(species.act.m1, type = 2) 
    # because the three way interaction is not significant after monte carlo permutation
    # interactions are also not significant when running the type III so preceded with type II 
    drop1(species.act.m1)
   
    species.act.m2 <- lm(full.act.data$mean.both ~
                         full.act.data$Temperature*as.numeric(full.act.data$DateTimePOS) +
                           full.act.data$Temperature*full.act.data$species + 
                           as.numeric(full.act.data$DateTimePOS)*full.act.data$species)
    
    Anova(species.act.m2, type = 3) # becuase of significant interaction
    anova(species.act.m1,  species.act.m2, test = "LRT")
    # Model 1 - full model with three way interaction is the best model according to LRT
    
## Test Assumptions  
  # Test for Autocorrelation: Because this is a repeated measures 
  acf(species.act.m1$residuals) # No autocorrelation
  
  # plot data to evaluate assumptions
  par(mfrow = c(2,2))
  plot(species.act.m1)
  qqnorm(species.act.m1$residuals)
  qqline(species.act.m1$residuals)
  hist(species.act.m1$residuals)
  
  # test for normality using shapiro-wilk test
  shapiro.test(species.act.m1$residuals) # significant value - not normal 

```


## Monte Carlo
Run a Monte Carlo for full model with species complex, time and temperature
```{r}

####################
#### Full Model ####
####################
  alpha <- 0.05  # for 95% confidence interval
  bootstrap <- 999
  new_act <- numeric(length(bootstrap))
  fvalues <- matrix(nrow = 999, ncol = 7)
  colnames(fvalues) <- c("Temp", "Time", "Species", "Temp*Time", "Temp*Species", "Time*Species", "Temp*Time*Species")

  for(i in 1:bootstrap){
    #new_y <- sample(full.act.data$mean.both, replace = TRUE)
    new_act <- lm(sample(full.act.data$mean.both) ~ 
                    sample(full.act.data$Temperature)*sample(as.numeric(full.act.data$DateTimePOS))*
                    sample(full.act.data$species))
    fvalues[i,] <- summary(aov(new_act))[[1]][["F value"]][1:7]
  }

   for(i in 1:bootstrap){
    #new_y <- sample(full.act.data$mean.both, replace = TRUE)
    new_act <- lm(sample(full.act.data$mean.both) ~ 
                    sample(full.act.data$Temperature)*sample(as.numeric(full.act.data$DateTimePOS))*
                    sample(full.act.data$species))
    fvalues[i,] <- Anova(new_act, type = 2)[["F value"]][1:7]
  }
  
  fvalues <- as.data.frame(fvalues)
  fval.means <- colMeans(fvalues)
  lowCI <- numeric(length(ncol(fvalues)))
  upCI <- numeric(length(ncol(fvalues)))
  for(i in 1:ncol(fvalues)){
    lowCI[i] <- quantile(fvalues[,i], alpha/2, type = 1)
    upCI[i] <- quantile(fvalues[,i], 1-alpha/2, type = 1)
  }

  mont.carloData <- cbind(fval.means, lowCI, upCI, summary(aov(species.act.m1))[[1]][["F value"]][1:7])
  mont.carloData <- cbind(fval.means, lowCI, upCI, Anova(species.act.m1, type = 2)[["F value"]][1:7])
  mont.carloData
  ## A value higher than the upper CI indicates significance 

```


## Separate data by species complex and rerun analysis
```{r}

 ## Black Rockfish
  blk.act.m1 <- lm(complete.act.data$mean.both~complete.act.data$Temperature*as.numeric(complete.act.data$DateTimePOS) 
                   + complete.act.data$Temperature*as.numeric(complete.act.data$DateTimePOS))
  summary(aov(blk.act.m1))
  summary(blk.act.m1)
  drop1(blk.act.m1)
  
  blk.act.m2 <- lm(complete.act.data$mean.both~complete.act.data$Temperature + as.numeric(complete.act.data$DateTimePOS))
  summary(aov(blk.act.m2))
  Anova(blk.act.m2, type = 2)
  drop1(blk.act.m2)
  
   anova(blk.act.m2, blk.act.m1, test = "LRT")
    # Model 2 - better model due to non-significant interaction
   
  ## Copper Rockfish
  cp.act.m1 <- lm((complete.act.data.cp$mean.both)^2~
                     complete.act.data.cp$Temperature*as.numeric(complete.act.data.cp$DateTimePOS))
  shapiro.test(cp.act.m1$residuals)
  Anova(cp.act.m1, type = 3)
  # type III sums of squares due to a significant interaction
  summary(cp.act.m1)
  drop1(cp.act.m1)


```


```{r}

##########################
#### BY Complex Model ####
##########################
alpha <- 0.05  # for 95% confidence interval
bootstrap <- 999
new_act.by <- numeric(length(bootstrap))
fvalues.by <- matrix(nrow = 999, ncol = 2)
colnames(fvalues.by) <- c("Temp", "Time")

for(i in 1:bootstrap){
  #new_y <- sample(full.act.data$mean.both, replace = TRUE)
  new_act.by <- lm(sample(complete.act.data$mean.both)~sample(complete.act.data$Temperature) + 
                     sample(as.numeric(complete.act.data$DateTimePOS)))
  fvalues.by[i,] <- Anova(new_act.by, type = 2)[["F value"]][1:2]
}

fvalues.by <- as.data.frame(fvalues.by)
fval.means.by <- colMeans(fvalues.by)
lowCI.by <- numeric(length(ncol(fvalues.by)))
upCI.by <- numeric(length(ncol(fvalues.by)))
for(i in 1:ncol(fvalues.by)){
  lowCI.by[i] <- quantile(fvalues.by[,i], alpha/2, type = 1)
  upCI.by[i] <- quantile(fvalues.by[,i], 1-alpha/2, type = 1)
}

mont.carloData.by <- cbind(fval.means.by, lowCI.by, upCI.by, Anova(blk.act.m1, type = 2)[["F value"]][1:2])
mont.carloData.by

##########################
#### CQ Complex Model ####
##########################
alpha <- 0.05  # for 95% confidence interval
bootstrap <- 999
new_act.cq <- numeric(length(bootstrap))
fvalues.cq <- matrix(nrow = 999, ncol = 4)
colnames(fvalues.cq) <- c("Intercept", "Temp", "Time","Temp*Time")

for(i in 1:bootstrap){
  #new_y <- sample(full.act.data$mean.both, replace = TRUE)
  new_act.cq <- lm(sample(complete.act.data.cp$mean.both)~sample(complete.act.data.cp$Temperature) + 
                     sample(as.numeric(complete.act.data.cp$DateTimePOS)) + 
                     sample(complete.act.data.cp$Temperature*as.numeric(complete.act.data.cp$DateTimePOS)))
  fvalues.cq[i,] <- Anova(new_act.cq, type = 3)[["F value"]][1:4]
                         
}

fvalues.cq <- as.data.frame(fvalues.cq)
fval.means.cq <- colMeans(fvalues.cq)
lowCI.cq <- numeric(length(ncol(fvalues.cq)))
upCI.cq <- numeric(length(ncol(fvalues.cq)))
for(i in 1:ncol(fvalues.cq)){
  lowCI.cq[i] <- quantile(fvalues.cq[,i], alpha/2, type = 1)
  upCI.cq[i] <- quantile(fvalues.cq[,i], 1-alpha/2, type = 1)
}

mont.carloData.cq <- cbind(fval.means.cq, lowCI.cq, upCI.cq, Anova(cp.act.m1, type = 3)[["F value"]][1:4])
mont.carloData.cq
```

